On the Bit Complexity of Finding Points in Connected Components of a Smooth Real Hypersurface

### 2020-02-05 main.tex
stuff

Throughout this section, we consider that $i \in \{1,\hdots,n\}$ is
fixed. We prove that there exists a hypersurface $\D_{3,i} \subset
\C^{n^2}$ such that if $\mA$ is not in $\D_{3,i}$, then $\mA$ is
invertible and satisfies $\textbf{H}_i(1)$ and $\textbf{H}_i(2)$.

Let $\A$ be an $n \times n$ matrix of new indeterminates
$(\A_{i,j})_{1 \leq i , j \leq n}.$ Define $f^{\A} \in
\mathbb{Q}(\A)[\textbf{X}]$ as $f(\A\textbf{X})$ and $V^\A=V(f^\A).$
Recall from Section 4.1.4 that $f^\A$ satisfies
$\textbf{H}_i^{'}(1),\textbf{H}_i^{'}(2),$ and $\textbf{H}_i^{'}(3).$
, to simplify notation, let $\I^\A$ denote
$\I(\pi_i,V^\A)$ and let $W^\A$ denote $W(\pi_i,V^\A).$ Furthermore,
throughout this section, We will avoid writing $i$ where the context is clear.
%
\subsection{Sketch of the proof}
%
Let $f \in \mathbb{Q}[X_1,\hdots,X_n]$ have total degree $D$. Assume $f$ satisfies \textbf{H}, so that $f$ is squarefree with $V(f)$ smooth. Recall $\textbf{H}_i^{'}(7):$ \textit{$W(\pi_i,V)$ is in Noether position for $\pi_{i-1}$}, which is equivalent to having the extension
\C[\textbf{X}_{\leq i-1}]\rightarrow\C[\textbf{X}]/\frak{I}(\pi_i,V)
injective and  integral.
\begin{theorem}
There exists a hypersurface $\Delta_3 \subset \C^{n^2}$ of degree at most $\td$ with the property that, if $A \in \C^{n^2} - \Delta_3$ then, for each $i \in\{1,\hdots,n\}, f^A$ satisfies $\textbf{H}_i'(7)$.
\end{theorem}
Section 7 is devoted to proving Theorem 7.1. It has already been shown in \cite{EMP} that $f^A$ satisfies $\textbf{H}_i^{'}(7)$ for a generic change of variables. The new contribution is in upper bounding the degree of $\Delta_3.$
The ring extension \[\mathbb{Q}(\frak{A})[\textbf{X}_{\leq i-1}]\rightarrow\mathbb{Q}(\frak{A})[\textbf{X}]/\I^{\A}\] is integral.

>>>>

Throughout this section,  $i \in \{1,\hdots,n\}$ is
fixed. We prove that there exists a hypersurface $\D_{3,i} \subset
\C^{n^2}$ such that if $\mA$ is not in $\D_{3,i}$, then $\mA$ is
invertible and satisfies $\textbf{H}_i$ and $\textbf{H}_i$.

Since $i$ is fixed, to simplify notation, let $\I^\A$ denote
$\I(\pi_i,V^\A)$ and let $W^\A$ denote $W(\pi_i,V^\A).$

Consider again the matrix of indeterminates $\A$.  Define $f^{\A} \in
\mathbb{Q}(\A)[\textbf{X}]$ as $f(\A\textbf{X})$ and $V^\A=V(f^\A).$
Recall from Section~\ref{xxx} that $f^\A$ satisfies
$\textbf{H}_i^{'}(1)$, that is, \td.

\[
\C[\textbf{X}_{\leq i-1}]\rightarrow\C[\textbf{X}]/\frak{I}(\pi_i,V)
\]
injective and  integral.
%

It has already been shown in \cite{EMP} that $f^A$ satisfies
$\textbf{H}_i^{'}(7)$ for a generic change of variables. The new
contribution is in upper bounding the degree of $\Delta_3.$

\begin{lemma} 
The ring
extension \[\mathbb{Q}(\frak{A})[X_1,\dots,X_{i-1}]\rightarrow\mathbb{Q}(\frak{A})[X_1,\dots,X_n]/\I^{\A}\]
\end{lemma}
